In today's capitalist world, stocks present an attractive avenue for financial gain, offering significant profit potential. 
Investors, regardless of their depth of understanding of the stock market, are constantly seeking reliable methods to predict future stock prices, as their financial well-being often hinges on these predictions.

Predicting stock prices is fundamentally about discerning the real value of a company. 
Knowing a company's true value helps in determining whether its stock price will rise or fall from its current level. 
However, this is a complex task influenced by a myriad of factors, including global events and economic conditions.

Historically, professional fund managers have been pivotal in guiding investments in the stock market. 
However, their strategies and predictions are susceptible to personal biases. 

While numerous services today use machine learning for this purpose, many are not open-source and are primarily geared towards professional investors. 
These systems, often complex and tailored for experienced users, focus more on asset allocation than on precise stock price prediction. 
In contrast, our project targets the general public, who rely more on simple chart analysis and intuition, without delving deep into a company's fundamentals or news events.

Our proposal is to predict the short-term movement of blue-chip stocks, a strategy known to be effective over periods ranging from a few days to a few months. 
We aim to make short-term predictions, not in real-time, to assist general users and simplify the prediction process.

To achieve this, we have employed machine learning techniques, utilizing models such as Long Short-Term Memory(LSTM), Gated Recurrent Unit(GRU), and Transformer. 
These models have been instrumental in successfully predicting stock prices for the next few days by capturing short-term trends. 
In addition, we have integrated VADER, a sentiment analysis tool, to reflect recent issues and capture both short- and long-term stock price changes based on current events.

Our system has been deployed as a publicly accessible web service, offering users easy access to our predictive model. 
This deployment significantly contributes to investment decision-making, lowering the entry barrier for those interested in stock market investments. 
Empirical evaluations of our system have shown promising results in capturing short-term trend of stock price movements, thereby validating our approach and offering a valuable tool for investors.